Function to find association b/w n significant eigen genes with Diagnosis, Diagnosis.Gender, ApoE

### 2017-10-09 code/Rmd/networkAssociationTest.Rmd
Added markdown

  # Function to get PCs
  getPCs <- function(expr){
    pc = prcomp(expr, center = T, scale. = T)
    pc.sdev = pc$sdev^2/sum(pc$sdev^2)
    ind = which(pc.sdev >= 0.01)
    pc.sdev = pc.sdev[ind]
    pc.rot = pc$rotation[,ind, drop = F]

@@

p = ggplot(Dx, aes(x = method, y = pc1.eff.sz, color = -log10(pc1.fdr))) + geom_boxplot() + geom_jitter()
p = p + coord_flip() + facet_grid(.~brainRegion, scales = 'free_x')  + xlab('Method') + ylab('PC1 Effect Size')
p = p + scale_color_continuous(low = 'white', high = 'red')
p + theme(legend.position = 'top')
```
Top 5 modules per method
```{r Dx.1, fig.height=12, fig.width=12}
# Top 5 in each method
h = lapply(unique(Dx$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion, method) %>%
    dplyr::filter(total.fdr <= 0.05) %>%
    dplyr::top_n(5, total.eff.sz) %>%
    dplyr::top_n(5, pc1.eff.sz) %>%
    dplyr::filter(brainRegion == br)

@@

p = ggplot(Dx.gender, aes(x = method, y = pc1.eff.sz, color = -log10(pc1.fdr))) + geom_boxplot() + geom_jitter()
p = p + coord_flip() + facet_grid(.~brainRegion, scales = 'free_x')  + xlab('Method') + ylab('PC1 Effect Size')
p = p + scale_color_continuous(low = 'white', high = 'red')
p + theme(legend.position = 'top')
```
Top 5 modules per method
```{r Dx.gender.1, fig.height=12, fig.width=12}
# Top 5 in each method
h = lapply(unique(Dx.gender$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion, method) %>%
    dplyr::filter(total.fdr <= 0.05) %>%
    dplyr::top_n(5, total.eff.sz) %>%
    dplyr::top_n(5, pc1.eff.sz) %>%
    dplyr::filter(brainRegion == br)

  print(dim(imp.mods)[1])
  print(br)

  if(dim(imp.mods)[1] != 0 ){
    getOverlapPlots(imp.mods, MOD.MEMBERS, MODULE.OVRLP)
  }
}, Dx.gender, MOD.MEMBERS, MODULE.OVRLP)
draw(h[[1]], heatmap_legend_side='left')
# draw(h[[2]], heatmap_legend_side='left')
draw(h[[3]], heatmap_legend_side='left')
draw(h[[4]], heatmap_legend_side='left')
draw(h[[5]], heatmap_legend_side='left')
draw(h[[6]], heatmap_legend_side='left')
draw(h[[7]], heatmap_legend_side='left')
```
Top 5 modules any method
```{r Dx.gender.2, fig.height=12, fig.width=12}
# Top 5 any method
h = lapply(unique(Dx.gender$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion) %>%
    dplyr::filter(total.fdr <= 0.05) %>%
    dplyr::top_n(25, total.eff.sz) %>%
    dplyr::top_n(25, pc1.eff.sz) %>%
    dplyr::filter(brainRegion == br)
  print(dim(imp.mods)[1])
  print(br)

@@

ggplot(all.rank, aes(x = other, y = magma))+geom_point()+facet_grid(.~brainRegion)+geom_smooth(method = 'lm')
```
Top 5 modules per method
```{r imp.mdl.1, fig.height=12, fig.width=12}
# Top 5 in each method
h = lapply(unique(all.rank$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion, method) %>%
    dplyr::top_n(5, rnk) %>%
    dplyr::top_n(5, Dx) %>%
    dplyr::filter(brainRegion == br)

@@

### Store results in synapse
```{r syn.store, include=FALSE}
CODE = Folder('Network Association Tests', parentId = "syn10306449")
CODE = synStore(CODE)

write.table(Dx, file = 'AssociaitonStatWithDx.tsv', sep = '\t', quote = F, row.names = F)
OBJ = File('AssociaitonStatWithDx.tsv', name = 'Association with Dx', parentId = CODE@properties$id)
OBJ = synStore(OBJ, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Dx.gender, file = 'AssociaitonStatWithDxGender.tsv', sep = '\t', quote = F, row.names = F)
OBJ1 = File('AssociaitonStatWithDxGender.tsv', name = 'Association with Dx.Gender', parentId = CODE@properties$id)
OBJ1 = synStore(OBJ1, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(ApoE, file = 'AssociaitonStatWithApoE4.tsv', sep = '\t', quote = F, row.names = F)
OBJ2 = File('AssociaitonStatWithApoE4.tsv', name = 'Association with ApoE4', parentId = CODE@properties$id)
OBJ2 = synStore(OBJ2, used = all.used.ids, executed = thisFile, activityName = activityName)

save(list = c('assoc.stat.diagnosis', 'assoc.stat.diagnosis.gender', 'assoc.stat.apoe'), file = 'AllAssociationResults.RData')
OBJ3 = File('AllAssociationResults.RData', name = 'All Assocition Statistics (RData)', parentId = CODE@properties$id)
OBJ3 = synStore(OBJ3, used = all.used.ids, executed = thisFile, activityName = activityName)
```

>>>>

  # Function to get PCs
  getPCs <- function(expr){
    expr = scale(t(scale(t(expr))))
    pc = prcomp(expr, center = F, scale. = F)
    pc.sdev = pc$sdev^2/sum(pc$sdev^2)
    ind = which(pc.sdev >= 0.01)
    pc.sdev = pc.sdev[ind]
    pc.rot = pc$rotation[,ind, drop = F]

@@

p = ggplot(Dx, aes(x = method, y = pc1.eff.sz, color = -log10(pc1.fdr))) + geom_boxplot() + geom_jitter()
p = p + coord_flip() + facet_grid(.~brainRegion, scales = 'free_x')  + xlab('Method') + ylab('PC1 Effect Size')
p = p + scale_color_continuous(low = 'white', high = 'red')
p + theme(legend.position = 'top')

writeLines('Number of significantly associated modules')
Dx %>%
  dplyr::group_by(brainRegion, method) %>%
  dplyr::summarise(nsig = sum(total.fdr <= 0.05)) %>%
  tidyr::spread(method, nsig) %>%
  kable()

writeLines('Percent of significantly associated modules')
Dx %>%
  dplyr::group_by(brainRegion, method) %>%
  dplyr::summarise(nsig = round(sum(total.fdr <= 0.05)/sum(total.fdr <= 1) * 100, 2)) %>%
  tidyr::spread(method, nsig) %>%
  kable()

writeLines('Percent of modules whose PC1 is significantly associated')
Dx %>%
  dplyr::group_by(brainRegion, method) %>%
  dplyr::summarise(nsig = round(sum(pc1.fdr <= 0.05)/sum(pc1.fdr <= 1) * 100, 2)) %>%
  tidyr::spread(method, nsig) %>%
  kable()
```
Top 5 modules per method
```{r Dx.1, fig.height=12, fig.width=12}
# Top 5 in each method
h = lapply(unique(Dx$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion, method) %>%
    dplyr::filter(total.fdr <= 0.05) %>%
    dplyr::top_n(5, total.eff.sz) %>%
    dplyr::top_n(5, pc1.eff.sz) %>%
    dplyr::filter(brainRegion == br)

@@

p = ggplot(Dx.gender, aes(x = method, y = pc1.eff.sz, color = -log10(pc1.fdr))) + geom_boxplot() + geom_jitter()
p = p + coord_flip() + facet_grid(.~brainRegion, scales = 'free_x')  + xlab('Method') + ylab('PC1 Effect Size')
p = p + scale_color_continuous(low = 'white', high = 'red')
p + theme(legend.position = 'top')

writeLines('Number of significantly associated modules')
Dx.gender %>%
  dplyr::group_by(brainRegion, method) %>%
  dplyr::summarise(nsig = sum(total.fdr <= 0.05)) %>%
  tidyr::spread(method, nsig) %>%
  kable()

writeLines('Percent of significantly associated modules')
Dx.gender %>%
  dplyr::group_by(brainRegion, method) %>%
  dplyr::summarise(nsig = round(sum(total.fdr <= 0.05)/sum(total.fdr <= 1) * 100, 2)) %>%
  tidyr::spread(method, nsig) %>%
  kable()

writeLines('Percent of modules whose PC1 is significantly associated')
Dx.gender %>%
  dplyr::group_by(brainRegion, method) %>%
  dplyr::summarise(nsig = round(sum(pc1.fdr <= 0.05)/sum(pc1.fdr <= 1) * 100, 2)) %>%
  tidyr::spread(method, nsig) %>%
  kable()
```
Top 5 modules per method
```{r Dx.gender.1, fig.height=12, fig.width=12}
# Top 5 in each method
h = lapply(unique(Dx.gender$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion, method) %>%
    dplyr::filter(total.fdr <= 0.05) %>%
    dplyr::top_n(5, total.eff.sz) %>%
    dplyr::top_n(5, pc1.eff.sz) %>%
    dplyr::filter(brainRegion == br)

  if(dim(imp.mods)[1] != 0 ){
    getOverlapPlots(imp.mods, MOD.MEMBERS, MODULE.OVRLP)
  }
}, Dx.gender, MOD.MEMBERS, MODULE.OVRLP)
draw(h[[1]], heatmap_legend_side='left')
draw(h[[2]], heatmap_legend_side='left')
draw(h[[3]], heatmap_legend_side='left')
draw(h[[4]], heatmap_legend_side='left')
draw(h[[5]], heatmap_legend_side='left')
draw(h[[6]], heatmap_legend_side='left')
draw(h[[7]], heatmap_legend_side='left')
```
Top 5 modules any method
```{r Dx.gender.2, fig.height=12, fig.width=12}
# Top 5 any method
h = lapply(unique(Dx.gender$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion) %>%
    dplyr::filter(total.fdr <= 0.05) %>%
    dplyr::top_n(25, total.eff.sz) %>%
    dplyr::top_n(25, pc1.eff.sz) %>%
    dplyr::filter(brainRegion == br)

@@

ggplot(all.rank, aes(x = other, y = magma))+geom_point()+facet_grid(.~brainRegion)+geom_smooth(method = 'lm')

ggplot(tmp, aes(x = method, y = rnk)) + geom_boxplot() + facet_grid(.~brainRegion) + theme(axis.text.x = element_text(angle=45, hjust = 1)) + coord_flip() + geom_jitter()

```
Top 5 modules per method
```{r imp.mdl.1, fig.height=12, fig.width=12}
# Top 5 in each method
h = lapply(unique(all.rank$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion, method) %>%
    dplyr::top_n(5, rnk) %>%
    dplyr::top_n(5, Dx) %>%
    dplyr::filter(brainRegion == br)

@@

### Store results in synapse
```{r syn.store, include=FALSE}
write.table(Dx, file = 'AssociaitonStatWithDx.tsv', sep = '\t', quote = F, row.names = F)
OBJ = File('AssociaitonStatWithDx.tsv', name = 'Association with Dx', parentId = 'syn10831307')
OBJ = synStore(OBJ, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Dx.gender, file = 'AssociaitonStatWithDxGender.tsv', sep = '\t', quote = F, row.names = F)
OBJ1 = File('AssociaitonStatWithDxGender.tsv', name = 'Association with Dx.Gender', parentId = 'syn10831307')
OBJ1 = synStore(OBJ1, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(ApoE, file = 'AssociaitonStatWithApoE4.tsv', sep = '\t', quote = F, row.names = F)
OBJ2 = File('AssociaitonStatWithApoE4.tsv', name = 'Association with ApoE4', parentId = 'syn10831307')
OBJ2 = synStore(OBJ2, used = all.used.ids, executed = thisFile, activityName = activityName)

save(list = c('assoc.stat.diagnosis', 'assoc.stat.diagnosis.gender', 'assoc.stat.apoe'), file = 'AllAssociationResults.RData')
OBJ3 = File('AllAssociationResults.RData', name = 'All Assocition Statistics (RData)', parentId = 'syn10831307')
OBJ3 = synStore(OBJ3, used = all.used.ids, executed = thisFile, activityName = activityName)
```
